\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
finished full spell check.
explain meaning of vT in Eq. (15)

  ,

@@

while in models with Higgs triplets the relation looks like

@@

      g_2^2v_T^2}{\left(M_{Z,\text{susy}}^{\text{\DRbar}}(M_Z)\right)^2}}.

@@

@@

The next step is to write a substitute for
the low-energy boundary condition class.
It must be declared as a descendent of \code{Constraint<Two_scale>}
whose function is described in \secref{sec:boundary-conditions}:
% MSSMcbs_two_scale_low_scale_constraint.hpp
\begin{numlstlisting}
#include "two_scale_constraint.hpp"

>>>>

  .

@@

In a model with a Higgs triplet the relation looks like

@@

      g_2^2v_T^2}{\left(M_{Z,\text{susy}}^{\text{\DRbar}}(M_Z)\right)^2}},

@@

where $v_T$ is the vacuum expectation value of the scalar Higgs
triplet field.

@@

The next step is to write a substitute for
the low-energy boundary condition class.
It must be declared as a descendant of \code{Constraint<Two_scale>}
whose function is described in \secref{sec:boundary-conditions}:
% MSSMcbs_two_scale_low_scale_constraint.hpp
\begin{numlstlisting}
#include "two_scale_constraint.hpp"
